### 2018-05-17 Sections/economics_of_the_quantum_internet.tex
Economics essay

It is evident from the flow of Alg.~\ref{alg:quant_coin} that the mining process now comprises solving an actual quantum computation of intrinsic value to Alice, since she is exchanging assets (e.g dollars or already-existing QuantCoins) in exchange for the computation. Completion of the computation followed by successful verification then further rewards Bob with a fresh QuantCoin\texttrademark\, courtesy of the distributed Blockchain algorithm.

The described protocol, in addition to mining a new coin, associated with the execution of a computation, acts as a currency converter for converting traditional assets (e.g dollars) into QuantCoins. This ability to currency convert is necessary, and completely differs from the original Bitcoin mining process, where coins are fabricated out of thin air by anyone and everyone, independent of their pre-existing monetary wealth -- Bitcoins are not created via conversion from any existing asset. The fact that the computation associated with each QuantCoin\texttrademark\, is of intrinsic value on the other hand, implies that Alice ought to be paying something for the service.

@@

What relationships characterise the value of QuantCoins? First, in a perfectly efficient market (Sec.~\ref{post:market_eff}) we have,
\begin{align}\label{eq:value_quantcoins}
	&(\text{Dollar value of a QuantCoin\texttrademark\,}) \nonumber\\
	&+ (\text{Dollar value of reward paid by Alice for execution}) \nonumber\\
	&= (\text{Dollar value of cost of execution for Bob}).
\end{align}

>>>>

It is evident from the flow of Alg.~\ref{alg:quant_coin} that the mining process now comprises solving an actual quantum computation of intrinsic value to Alice, since she is exchanging assets (e.g dollars or already-existing QuantCoins\texttrademark) in exchange for the computation. Completion of the computation followed by successful verification then further rewards Bob with a fresh QuantCoin\texttrademark\, courtesy of the distributed Blockchain algorithm.

The described protocol, in addition to mining a new coin, associated with the execution of a computation, acts as a currency converter for converting traditional assets (e.g dollars) into QuantCoins\texttrademark. This ability to currency convert is necessary, and completely differs from the original Bitcoin mining process, where coins are fabricated out of thin air by anyone and everyone, independent of their pre-existing monetary wealth -- Bitcoins are not created via conversion from any existing asset. The fact that the computation associated with each QuantCoin\texttrademark\, is of intrinsic value on the other hand, implies that Alice ought to be paying something for the service.

@@

What relationships characterise the value of QuantCoins\texttrademark? First, in a perfectly efficient market (Sec.~\ref{sec:eff_markets}) we have,
\begin{align}\label{eq:value_quantcoins}
	&(\text{Dollar value of a QuantCoin\texttrademark\,}) \nonumber\\
	&+ (\text{Dollar value of reward paid by Alice for execution}) \nonumber\\
	&= (\text{Dollar value of cost of execution for Bob}).
\end{align}
